\section{Introduction}
\subsection{Motivation}
In logistics a special class of goods exists which contributes majorly to its total delivery cost not due to its weight but due to its time criticality.

A life threatening example includes 
Medical supplies eg.  red blood cells (RBCs), Plasma, Cryoprecipitate, platelets, vaccines, diagnostic samples \cite{guinea}. These can be required during life threatening scenarios such as  combat casualty \cite{gilmore2019autonomous}, Hemorrhage during childbirth \cite{zipline_mit}  and Vaccines during disasters. Time criticality dictates the requirements for closer last mile hubs. Additionally Blood products have very low shelf life($\sim$42 days) \cite{blood_storage}  and special storage conditions eg. -18 \textcelsius{} for Cryoprecipitate \cite{blood_storage} which leads to inefficient distribution and wastage. Companies like Zipline\cite{zipline_rwanda}, Wingcopter\cite{wingcopter_vanuatu}, DHL\cite{dhl_tanzania} send medicines and vaccines to remote villages where road transport is too slow.

Much less life threatening but wider use case is of meal delivery. Online meal ordering is growing 300\% faster than dine-in traffic \cite{meal_300} since 2014 in USA. In India, food delivery platforms UberEats, Zomato and Swiggy combined serves on avg. $\sim$4 millions orders daily \cite{india_daily}. Online food delivery market is projected to reach \textdollar 134.5 billion by 2023 \cite{billion_2023}.

Current model of delivery involves a person delivering a meal(usually singular) on a ground vehicle (bike or car). Energy inefficiecy is evident as overhead of $\sim$ 180 Kg (person + bike) needs to undergo trip to deliver relatively small meal, say pizza $\sim$ 0.6 Kg \cite{dominos}. Major cost is contributed by human workforce due to absence of autonomy. Additionally, use of ground vehicles contributes to traffic congestion. Radius of operation(distance b/w user and restaurants) for restaurants remains small ($\sim$5km)  constraint put by delivery time($\sim$35 mins) \cite{swiggy_radius}.

Above inefficiencies thus motivates delivery industry (Google Wing \cite{google_wing_last_mile}, Amazon Prime Air\cite{prime_air}, Uber Elevate \cite{uber_eats_drone}) to adopt UAVs for last mile logistics of light goods.

%\subsection{Applications of UAVs}
% brief on UAV use cases in diff. industries. an image and line about motivation. eg. companies.
% aerial photograph
% power line inspection
% traffic surveylence
% mine inspection
% oil pipes inspection
% wind farm blade inspection
% agriculture (dusting and pesticide spraying)
% search and rescue


% \noindent\fbox{%
% \textbf{Note to reader}
% % note to reader
% \parbox{textwidth}{%
% Since UAVs demands diversity in engineering disciplines(aeronautics for UAV design, electrical for sensors, communication, mechanical for control and motion planning, Computer science for Visual perception and simulation testbed design), this report serves as nascent overview of state of each component. Relevant texts, courses, papers and software packages are cited to assist reader to explore deeper. This report is a mere reflection of the journey of author, in attempt to explore this field. Reprint of this text with possible corrections and review by subject experts is expected. Hence, beginner reader is requested to take caution while advanced reader(reviewer), please forgive naiveness of author. Review corrections are welcome by email/ google docs comments or any other means convenient, and are greatly appreciated by author.
% }%
\subsection{Outline}
% preface to sections of this report
